A survey of generic IND-CCA2 transformations

### 2024-07-07 faster-fo-transform/cca-transform-survey/main.tex
well known result: ind-cpa security implies ow-cpa security

@@

\section{Modular Fujisaki-Okamoto transformation}
The Fujisaki-Okamoto transformation \cite{fujisaki1999secure} and its KEM variations \cite{hofheinz2017modular}.

>>>>

\cite{hofheinz2017modular} stated a ``well-known'' result that the \monospace{IND-CPA} security of a scheme with a large message space implies \monospace{OW-CPA} security:

\begin{theorem}\label{thm:ind-cpa-implies-ow-cpa}
    For every \monospace{IND-CPA} adversary $B$ against some $\pke$, there exists an \monospace{OW-CPA} adversary $A$ against the same $\pke$ such that:

    \begin{equation*}
        \monospace{Adv}_\monospace{OW-CPA}(A) = \frac{1}{\norm{\mathcal{M}}} + \monospace{Adv}_\monospace{IND-CPA}(B)
    \end{equation*}
\end{theorem}

@@

\section{Modular Fujisaki-Okamoto transformation}
The Fujisaki-Okamoto transformation \cite{fujisaki1999secure} and its KEM variations \cite{hofheinz2017modular} achieve security against adaptive chosen-ciphertext attacks through \emph{de-randomization} and \emph{re-encryption}. In particular, the modular FO transformation contains two steps. First, the
